Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2021-10-07 paper/changes.tex
Reorganized the section on computational complexity.  Also removed (latex commented) the irrelevant part of pre-computation and parallelization since the comment has already been made earlier (now appears as a footnote).
Added the note about the code base in changes.pdf also
Added RMSE eq.
Also edited discussion on deep learning.
Edited DART related response, and RMSE-SSIM related response in changes.pdf.

\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
\usepackage{caption}
\usepackage{subcaption, tabularx}
\usepackage{xcolor}
\usepackage{boxedminipage}
\usepackage{a4wide}
\usepackage{subcaption}
\usepackage[colorlinks=true]{hyperref}
\title{Response to Reviewers and Associate Editor}
\begin{document}
\date{}
\maketitle

@@

 Among the family of algebraic techniques, we have compared our method
 with Algebraic Reconstruction Technique (ART)~\cite{art} and Simultaneous
 Algebraic Reconstruction Technique (SART)~\cite{sart}. We do not reconstruct
 using Discrete Algebraic Reconstruction Technique (DART)~\cite{dart} since there
 is no prior information about the number of possible attentuation
 coefficients in the test object.
%% IS THERE A NEED TO HIGHGLIHT what we have not done?  Also give references?
 Among other iterative techniques, we
 have used Simultaneous Iterative Reconstruction Technique (SIRT)~\cite{sirt},
 Total Variation (TV)~\cite{TV},~\cite{TVReg} and Compressed Sensing (CS)~\cite{lasso} with Haar wavelet
 and DCT as sparsity basis. The details of solvers used for these
 algorithms and their reconstructions are in Page.~7 (Section-6A) of
 the paper. For CS reconstruction, we observed that Haar wavelet and
 DCT were best suited for our dataset among various other possible
 sparsity basis.

@@

  The reason for not reporting RMSE stems from the optimization
  process in Equation~\ref{Eq:simple_TV}.

@@

  %% Why not combine all of the values in one table?

\begin{table}[!h]
  \centering
 \caption{RMSE of reconstructions from various
    methods within the RoI.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
&\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
\\ \hline \textbf{Potato}& 0.29 & 0.24 & \textcolor{red}{0.18}
\\ \hline \textbf{Sprouts}& 0.53 & 0.48 & \textcolor{red}{0.30}
\\ \hline \textbf{Liver}& 0.05 & 0.17 & \textcolor{red}{0.03}
\\ \hline
\end{tabular}
\label{table:rmse}
\end{table}

@@

  We now present details of both time and space complexities of our technique in Section.~7B of our paper.

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption, tabularx}
\usepackage{xcolor}
\usepackage{boxedminipage}
\usepackage{a4wide}
\usepackage{subcaption,comment}
\usepackage[colorlinks=true]{hyperref}
\title{Response to Reviewers and Associate Editor}
\begin{document}
\date{}
\maketitle

@@

 Among the family of algebraic techniques, we have compared our method
 with Algebraic Reconstruction Technique (ART)~\cite{art} and Simultaneous
 Algebraic Reconstruction Technique (SART)~\cite{sart}. In order to use the Discrete Algebraic Reconstruction Technique (DART)~\cite{dart}, one must assume the imaged object to be made of only a few fixed number of known attenuation coefficients. Since we do not make any such assumption about  our datasets, we have not used DART. %% IS THERE A NEED TO HIGHGLIHT what we have not done?  Also give references?
 Among other iterative techniques, we
 have used Simultaneous Iterative Reconstruction Technique (SIRT)~\cite{sirt},
 Total Variation (TV)~\cite{TV},~\cite{TVReg} and Compressed Sensing (CS)~\cite{lasso} with Haar wavelet
 and DCT as sparsity basis. The details of solvers used for these
 algorithms and their reconstructions are in Page.~7 (Section-6A) of
 the paper. For CS reconstruction, we observed that Haar wavelet and
 DCT were best suited for our dataset among various other possible
 sparsity basis.

@@

  We have now presented RMSE values for all reconstructions in Tables 1-5 of the main paper. Since RMSE corresponds to error in intensity values, we have used SSIM with a higher weightage to structure for the purpose of measuring error in preservation of structures in our reconstructions.
  \begin{comment}
  The reason for not reporting RMSE stems from the optimization
  process in Equation~\ref{Eq:simple_TV}.

@@

  %% Why not combine all of the values in one table?
\end{comment}

@@

We accept this point, and present details in Section.~7B of our paper.
We also provide the code to reproduce the compute time claimed.

### 2021-10-07 paper/post_tci.tex
Added RMSE eq.
Also edited discussion on deep learning.
Edited DART related response, and RMSE-SSIM related response in changes.pdf.

In this section, we first illustrate the advantage of using multiple
types of eigenspaces for the computation of weights map, and then
present reconstruction results on all datasets. For quantitative
evaluation, we compute the Structural Similarity Index Metric
(SSIM)~\cite{ssim}. Here, we assign higher importance to the
preservation of structure in a reconstruction by assigning the
following weights to structure, contrast and intensity respectively:
$0.7,0.2,0.1$. The reason for emphasizing the structure with an
exponent of 0.7 stems from the optimization process since the
intensity span (and, in general, the histogram) of reconstructed volumes
differ across various methods and solvers.

@@

%---------------------------------------
\begin{table}[!h]
  \centering
  \caption{The SSIM (RMSE) of reconstructed okra from various
    methods. SSIM of the ideal reconstruction is 1.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.46 (0.28)
& 0.50 (0.24) & \textcolor{red}{0.74 (0.15)} \\ \hline \textbf{3D, 30 views} & 0.69 (0.21) & 0.74 (0.30) & \textcolor{red}{0.78 (0.26)}\\
\hline \textbf{3D, 45 views} & 0.65 (0.22) & 0.70 (0.21) & \textcolor{red}{0.71 (0.19)}
\\ \hline
\end{tabular}
\label{table:okra_ssim}
\end{table}

@@

  Further, a specific `event-of-interest' may occur just once in a
  longitudinal study and hence training on data of all previous time
  instants may be misleading. If however, we use measurements from
  identical and full-cycle longitudinal studies, including
  events-of-interest, of similar specimen (instead of the `same'
  specimen as we used), a deep-learning technique may be applied. We
  see this as an extension of using object-prior generated from the
  same object.

@@

%--------------------------Conclusion-----------------------
\section{Conclusions}
\label{sec:conclusions}
This work deals with the effective use of priors for tomographic
reconstruction in longitudinal studies. When the number of measurements is
substantially low, we discuss the utility of
using information from previous scans of the same object, as outlined in
Fig.~\ref{fig:prior_overview}. In order to observe details of new changes
accurately, we use a novel
spatially-varying prior-based method. This method ensures that the
reconstruction of localized new information in the data is not
affected by the priors, while the other relatively stationary regions benefit from the extra prior information. %Based on the potato and the okra experiments,
%we see that our method is able to \emph{discover both} the presence of
%a new structure, as well as the absence of a structure.
We have thus
improved state of the art by detecting the strength and location
of these regions of change and
assigning low prior weights wherever necessary. The probability of
presence of a `new region' is enhanced considerably by a novel
combination of different reconstruction techniques.  We have validated
our technique on medical 2D and real, biological 3D datasets for
longitudinal studies. The method is also largely robust to the number
of previously scanned objects used. We urge the reader to see the
videos of reconstructed volumes in the supplementary
material~\cite{supp_paper}.
%Our method has been shown to make the best use of prior
%only when needed, thus detecting new changes of the test
%data.

>>>>

In this section, we first illustrate the advantage of using multiple
types of eigenspaces for the computation of weights map, and then
present reconstruction results on all datasets. For quantitative
evaluation, we use two metrics: the Root Mean Squared Error (RMSE) and the
Structural Similarity Index Metric (SSIM)~\cite{ssim}. If
$\boldsymbol{x}$ is the groundtruth data with $N$ voxels and
$\hat{\boldsymbol{x}}$ is the reconstructed data, then RMSE is
computed as follows

\begin{equation}
  \textrm{RMSE} =\sqrt{\frac{1}{N}\sum_{i=1}^N(\boldsymbol{x}(i) -
    \hat{\boldsymbol{x}}(i))^2}.
 \end{equation}

Since RMSE corresponds to error in intensity values, we have used SSIM
with a higher weightage to structure for the purpose of measuring
error in preservation of structures in our reconstructions. Hence, while
computing SSIM, we assign the following weights to structure, contrast
and intensity respectively: $0.7,0.2,0.1$.
%The reason for emphasizing the structure with an
%exponent of 0.7 stems from the optimization process since the
%intensity span (and, in general, the histogram) of reconstructed volumes
%differ across various methods and solvers.

@@

%---------------------------------------
\begin{table}[!h]
  \centering
  \caption{The SSIM (RMSE) within the RoI of reconstructed okra from various
    methods. SSIM of the ideal reconstruction is 1.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.46 (0.28)
& 0.50 (0.24) & \textcolor{red}{0.74 (0.15)} \\ 
\hline \textbf{3D} & 0.65 (0.22) & 0.70 (0.21) & \textcolor{red}{0.71 (0.19)}
\\ \hline
\end{tabular}
\label{table:okra_ssim}
\end{table}

@@

  Further, a specific `event-of-interest' may occur just once in a
  longitudinal study and hence training on data from all previous time
  instants of the same specimen may be misleading. As a future work, measurements from
  identical and full-cycle longitudinal studies, including
  events-of-interest, from an \textit{atlas of similar specimen} can be used to train
  a deep learning model.  We  see this as an extension of using object-prior generated from the
  \textit{same specimen}.

@@

%--------------------------Conclusion-----------------------
\section{Conclusions}
\label{sec:conclusions}
This work deals with the effective use of priors for tomographic
reconstruction in longitudinal studies. When the number of measurements is
substantially low, we discuss the utility of
using information from previous scans of the same object, as outlined in
Figs.~\ref{fig:story} and~\ref{fig:prior_overview}. In order to observe details of new changes
accurately, we use a novel
spatially-varying prior-based method. This method ensures that the
reconstruction of localized new information in the data is not
affected by the priors, while the other relatively stationary regions benefit from the extra prior information. %Based on the potato and the okra experiments,
%we see that our method is able to \emph{discover both} the presence of
%a new structure, as well as the absence of a structure.
We have thus
improved state of the art by detecting the strength and location
of these regions of change and
assigning low prior weights wherever necessary. The probability of
presence of a `new region' is enhanced considerably by a novel
combination of different reconstruction techniques.  We have validated
our technique on medical 2D and real, biological 3D datasets for
longitudinal studies. The method is also largely robust to the number
of previously scanned objects used. We urge the reader to see the
videos of reconstructed volumes in the supplementary
material~\cite{supp_paper}.
%Our method has been shown to make the best use of prior
%only when needed, thus detecting new changes of the test
%data.
